---
title: "Lab 0 - Hello R!"
author: "Kyra Chen"
date: "January 17, 2023"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(datasauRus)
```

Checking files

```{r}
datasaurus_dozen |>
  distinct(dataset)
```

## Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns. The three variables are dataset, x, and y.

## Exercise 2

```{r, fig.height= 5, fig.width= 5}
#| label: plot-dino
#| fig-height: 5
#| fig-width: 5

dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

```{r}
#| label: cor-dino
dino_data %>%
  summarize(r = cor(x, y))
```

## Exercise 3

```{r, fig.height= 5, fig.width= 5}
#| label: plot-circle
#| fig-height: 5
#| fig-width: 5

circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

```{r}
#| label: cor-circle
circle_data %>%
  summarize(r = cor(x, y))
```

The r value for the circle is slightly greater than that of the dino, although both values are extremely low.

## Exercise 4

```{r, fig.height= 5, fig.width= 5}
#| label: plot-star
#| fig-height: 5
#| fig-width: 5

star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

```{r}
#| label: cor-star
star_data %>%
  summarize(r = cor(x, y))
```

Once again the r value is extremely small. Like dino, the r value is \~ -0.06.

## Exercise 5

```{r, fig.height= 10, fig.width= 6}
#| label: plot_all
#| fig-height: 10
#| fig-width: 6

ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

The plots all have images created through data points that seem fairly random. They don't appear to have much of a correlation.

```{r}
#| label: cor-all
datasaurus_dozen |>
  group_by(dataset) |>
  summarize(r = cor(x, y)) 
```

The r values are all around -0.06, which is extremely small and supports my observation above that there's almost zero correlation in any of the plots.
